---
title: "CLC text mining"
output:
  html_document:
    pandoc_args:
    - +RTS
    - "-M64G"
    - "-RTS"
    code_folding: hide
    self_contained: no
    df_print: paged
    highlighter: haddock
    toc: true
    toc_float: true
    css: styles.css
    includes:
      in_header: header.html
---

<p>

<center><font size="3">`r Sys.Date()`</font></center>

</p>

```{r setup, include=FALSE}

#knitr::opts_chunk$set(fig.width = 5)
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages("pacman")
library(pacman)

p_load(sf,tidyverse,plotly,janitor,knitr,htmlwidgets,htmltools)
#rmapshaper,maps,tmap,nngeo

# rm(list = ls())

knitr::opts_knit$set(global.device = TRUE)

Sys.setlocale(locale = "C")

```

```{r data,include=FALSE}

load("tables/park_table1.Rda")
load("tables/wetlands_table.Rda")
load("tables/access_table.Rda")
load("tables/wetlandParks_v3_table1.Rda")
load("tables/wetlandParks_v3_table2.Rda")
load("tables/wetlandParks_v3_table3.Rda")
load("tables/wetlandParks_v1_table.Rda")

```


### WETLAND-PARKS


#### DATA:

##### [1] park polygons

[California Protected Areas Database](https://www.calands.org/) (parks and open spaces, filtered to coastal study area)

-   includes large (e.g., national forests) and small (e.g., neighborhood parks) open spaces
-   includes 2x categories of public access: open and restricted (i.e., requires permit or has limited hours of operation, but still publicly accessible)

```{r park polygons map code, eval=FALSE}

##### park polygon map
map_parks <- ggplot() +
  geom_sf(data=CA_clip, fill="grey92", color="grey92")+
  geom_sf(data=parks,
          aes(color=access_typ,
              fill=access_typ,
              text=paste(access_typ))) +
  scale_color_manual(values=c("thistle","plum4","honeydew3")) + 
  scale_fill_manual(values=c("thistle","plum4","honeydew3")) + 
  guides(fill=guide_legend(title = ""),color=guide_legend(title = "")) +
  theme_minimal()+
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),axis.text.y=element_blank(),axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(),panel.grid.minor = element_blank()) 

##### make interactive
ggplotly(map_parks, tooltip="text") %>%
  style(hoverlabel=list(font=list(family="IBM Plex Mono",size=11))) %>%
    layout(legend=list(x=0.5,xanchor='center',y=0,yanchor='top',orientation='h',
                       font=list(color="#32127a",family="IBM Plex Mono"))) 

```

```{r park polygons map, fig.width = 5, echo=FALSE, warning=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/map_parks.html", 
  scrolling = "no", 
  frameBorder = "0",
  height=550,
  width="100%"
)

#92
```

<p>

<center><font size="2"> *draw bounding box to zoom. click legend layers to toggle on/off.*</center></font>

</p>

<br>

```{r park polygons table1, echo=FALSE, warning=FALSE, cache=TRUE}

park_table1

```

<br>

##### [2] wetland polygons
[National Wetlands Inventory](https://www.fws.gov/program/national-wetlands-inventory/data-download) (filtered to "Estuarine and Marine Wetlands")

```{r wetland polygons code, eval=FALSE}

##### wetlands map
map_wetlands <- ggplot() +
    geom_sf(data=CA_clip, fill="grey92", color="grey92")+
  geom_sf(data=wetlands,
          aes(color=wetland_type,
              fill=wetland_type,
              text=paste(wetland_type))) +
  scale_fill_manual(values=c("emergent"="#a7dea2",
                             "scrub-shrub"="springgreen4")) +
  scale_color_manual(values=c("emergent"="#a7dea2",
                              "scrub-shrub"="springgreen4")) +
  guides(fill=guide_legend(title = ""),color=guide_legend(title = "")) +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) 

##### make interactive
ggplotly(map_wetlands,tooltip="none") %>%
  style(hoverlabel=list(font=list(family="IBM Plex Mono",size=11))) %>%
  layout(legend=list(x=0.5,xanchor='center',
                     y=0,yanchor='top',
                     orientation='h',
                     font=list(color="#32127a",family="IBM Plex Mono"))) 

```

```{r wetland polygons, fig.width = 5, echo=FALSE, warning=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/map_wetlands.html", 
  scrolling = "no", 
  frameBorder = "0",
  height=550,
  width="100%"
)

#120
```

<p>

<center><font size="2"> *draw bounding box to zoom.*</center>

</font>

</p>

<br>

```{r wetlands table, echo=FALSE, warning=FALSE, cache=TRUE}

wetlands_table

```

<br>

##### [3] coastal access points

[CA Coastal Commission](https://california-coastal-commission-open-data-1-3-coastalcomm.hub.arcgis.com/datasets/coastalcomm::public-access-points/about) (Olivia's extended dataset with Bay Area access points)

[to supplement park polygons w/ amenities data]

```{r access point map code, eval=FALSE}

##### CA commission map
map_access <- ggplot() +
  geom_sf(data=CA_clip, fill="grey92", color="grey92")+
  geom_sf(data=access,
          alpha=0.7,
          aes(color=wetland,
              text=paste(name))) +
  scale_color_manual(values=c("Yes"="aquamarine4",
                              "No"="grey65", 
                              "Unknown"="darkslateblue"))+ 
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) 

##### make interactive
ggplotly(map_access,tooltip="text") %>%
  style(hoverlabel=list(font=list(family="IBM Plex Mono",size=11))) %>%
  layout(legend=list(xref="paper",
                     x=0.5,xanchor='center',
                     y=0,yanchor='top',
                     orientation='h',traceorder="reversed",
                     title=list(font=list(color="#32127a",family="IBM Plex Mono")),
                     font=list(color="#32127a",family="IBM Plex Mono")))

```

```{r access point map, fig.width = 5, echo=FALSE, warning=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/map_access.html", 
  scrolling = "no", 
  frameBorder = "0",
  height=550,
  width="100%"
)

```

<p>

<center><font size="2"> *hover over points for site names. draw bounding box to zoom. click legend layers to toggle on/off.* </font></center>

</p>

<br>

```{r access point table, echo=FALSE, warning=FALSE, cache=TRUE}

access_table

```

<br>

#### STEPS

##### 1. filter NWI wetlands data to (1) emergent and (2) scrub-shrub estuarine intertidal zones, according to [NWI Classification Codes](https://www.fws.gov/sites/default/files/documents/wetlands-and-deepwater-map-code-diagram.pdf)

##### 2. select parks that intersect wetland polygons

```{r parks intersecting wetlands map code, eval=FALSE}

##### parks intersecting wetland polygon or wetland access point
wetlandParks_v3 <- parks %>%
  mutate(intersects_wetland= case_when(lengths(st_intersects(.,wetlands)) > 0 ~ "park intersects wetland")) %>%
  filter(!is.na(intersects_wetland)) %>%
  rename(suid=suid_nma,
         access_type=access_typ) %>%
  mutate(wetland_park="wetland-park")

##### wetland-park map
map_wetlandParks_v3 <- ggplot() +
    geom_sf(data=CA_clip, fill="grey92", color="grey92")+
  geom_sf(data=wetlandParks_v3,
          alpha=0.9,lwd=0.5,
          aes(fill=intersects_wetland,
              color=intersects_wetland,
              text=paste(unit_name)))+
  geom_sf(data=wetlands,
          alpha=0.4,lwd=0.25,
          aes(color=wetland,
              fill=wetland,
              text=paste(wetland))) +
  scale_fill_manual(values=c("wetland"="#a7dea2",
                             "park intersects wetland"="blueviolet")) +
  scale_color_manual(values=c("wetland"="#a7dea2",
                              "park intersects wetland"="blueviolet")) +
  guides(fill=guide_legend(title = ""),color=guide_legend(title = "")) +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) 

##### make interactive
ggplotly(map_wetlandParks_v3, tooltip="text") %>%
  style(hoverlabel=list(font=list(family="IBM Plex Mono",size=11))) %>%
    layout(legend=list(x=0.5,xanchor='center',
                     y=0,yanchor='top',
                     orientation='h',
                     font=list(color="#32127a",family="IBM Plex Mono"))) 

```

<br>

<center>TOTAL: **\~`r nrow(wetlandParks_v3_table1)`** wetland parks</center>

```{r parks intersecting wetlands map, fig.width = 5.5, echo=FALSE, warning=FALSE, cache=TRUE}

#### parks intersecting wetlands
tags$iframe(
  src = "figures/map_wetlandParks_v3.html", 
  scrolling = "no", 
  frameBorder = "0",
  height=550,
  width="100%"
)

```

<p>

<center><font size="2"> *hover over polygons for park names. draw bounding box to zoom. click legend layers to toggle on/off.* </font></center>

</p>

<br>

```{r parks intersecting wetlands table1, echo=FALSE, warning=FALSE, cache=TRUE}

wetlandParks_v3_table1

```

<br>

by access type:
```{r parks intersecting wetlands table2, echo=FALSE, warning=FALSE, cache=TRUE}

wetlandParks_v3_table2

```

<br>

by managing agency level:
```{r parks intersecting wetlands table3, echo=FALSE, warning=FALSE, cache=TRUE}

wetlandParks_v3_table3

```


<br>

#### OLD APPROACH

```{r old parks intersecting wetlands map code, eval=FALSE}

##### wetland-park map
map_wetlandParks_v1 <- ggplot() +
  geom_sf(data=CA_clip, fill="grey92", color="grey92")+
  geom_sf(data=wetlandParks_v1_simplified,
          # alpha=0.9,lwd=0.5,
          aes(fill=intersects_wetland,
              color=intersects_wetland,
              text=paste(unit_name)))+
  geom_sf(data=wetlands_simplified,
          alpha=0.5,lwd=0.3,
          aes(color=wetland,
              fill=wetland,
              text=paste(wetland))) +
  scale_fill_manual(values=c("park intersects wetland"="plum4",
                             "wetland"="#a7dea2")) +
  scale_color_manual(values=c("park intersects wetland"="plum4",
                              "wetland"="#a7dea2")) +
  guides(fill=guide_legend(title = ""),color=guide_legend(title = "")) +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) 

##### make interactive
ggplotly(map_wetlandParks_v1, tooltip="text") %>%
  style(hoverlabel=list(font=list(family="IBM Plex Mono",size=11))) %>%
  layout(legend=list(x=0.5,xanchor='center',
                     y=0,yanchor='top',
                     orientation='h',
                     font=list(color="#32127a",family="IBM Plex Mono")))

```

<br>

<center>TOTAL: **\~`r nrow(wetlandParks_v1_table)`** wetland parks</center>


```{r old parks intersecting wetlands map, fig.width = 5.5, echo=FALSE, warning=FALSE, cache=TRUE}

#### parks intersecting wetlands
tags$iframe(
  src = "figures/map_wetlandParks_v1.html", 
  scrolling = "no", 
  frameBorder = "0",
  height=550,
  width="100%"
)

```

<p>

<center><font size="2"> *hover over polygons for park names. draw bounding box to zoom. click legend layers to toggle on/off.* </font></center>

</p>

<br>

```{r parks old intersecting wetlands table, echo=FALSE, warning=FALSE, cache=TRUE}

wetlandParks_v1_table

```

<br>

### AMENITIES


### TRANSIT


### SOCIO-ECONOMIC
